Covariates analysis of MSBB RNASeq data of region BM 36

### 2016-05-01 code/Rmd/MSSM_BM_36_RNASeq.Rmd
Minor fix

FactorCovariates <- c('RACE','SEX','NP.1','bbscore','Dx','Batch')
ContCovariates <- c('PMI','AOD','PlaqueMean','RIN', 'RIN2')

@@

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                                dplyr::select(DESIGN,-one_of(colnames(DM1$design))),
                                                'all adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

>>>>

FactorCovariates <- c('RACE','SEX','Dx','Batch')
ContCovariates <- c('PMI','AOD','PlaqueMean','RIN', 'RIN2')

@@

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  tmp = sapply(dplyr::select(DESIGN,-one_of(colnames(DM1$design))), as.numeric)
  residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                                tmp, 'all adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)
